Topological order in the quantum dimer-pentamer model

### 2015-10-14 qdpm_paper.tex
small fix

    In this section we discuss the dimer dimer correlation function
    \begin{equation}
        C_{\mathrm{dimer}} = \langle d_0 d_r \rangle - \langle d_0 \rangle   \langle d_r \rangle   
        ,
    \end{equation}
    where $d_i$ is the ising degrees of freedom on link i.
    In order for the QDPM to exhibit topological order there we must find that it is in a gaped
    dimer liquid phase. It is likely that the QDPM in a liquid phase at the RK point because there 
    we find no evedence of broken symmetries in the system sizes up to $32x32$. As an example of the
    absence of broken symmetries we show
    the dimer correlation function measuered between a single dimer and all other dimers on the
    lattice in Fig.~\ref{fig:fig:dimer_gry_scale_qdpm} for a $16x16$ lattice.
    \subsection{Liquid}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{dimer_gry_scale_qdpm.pdf}
        \caption{Gray scale (actualy data) of the dimer corelation between the dimer in the upper
        left corner (colored red) and other dimers on a $16\times16$ lattice.}
        \label{fig:dimer_gry_scale_qdpm}
    \end{figure}

>>>>

    In this section we discuss the dimer dimer correlation function
    \begin{equation}
        C_{\mathrm{dimer}} = \langle d_0 d_r \rangle - \langle d_0 \rangle   \langle d_r \rangle   
        ,
    \end{equation}
    where $d_i$ is the ising degrees of freedom on link i.
    In order for the QDPM to exhibit topological order there we must find that it is in a gaped
    dimer liquid phase. It is likely that the QDPM in a liquid phase at the RK point because there 
    we find no evedence of broken symmetries in the system sizes up to $32x32$. As an example of the
    absence of broken symmetries we show
    the dimer correlation function measuered between a single dimer and all other dimers on the
    lattice in Fig.~\ref{fig:fig:dimer_gry_scale_qdpm} for a $16x16$ lattice.
    \subsection{Liquid}
    \begin{figure}[htpb]
        \centering
        \includegraphics[width=0.8\linewidth]{dimer_gry_scale_qdpm.pdf}
        \caption{Gray scale (actual data) of the dimer corelation between the dimer in the upper
        left corner (colored red) and all other dimers on a $16\times16$ lattice. The 
        dimers in the upperleft corner are colored red because they are off the scale shown at the
        botom of the figure.}
        \label{fig:dimer_gry_scale_qdpm}
    \end{figure}
